Towards a miniKanren with fair search strategies

### 2019-05-27 Paper/paper.tex
remove everything

\documentclass[format=acmlarge, review=true, authordraft=true]{acmart}

@@

\NOTE[LKC]{submission deadline: Mon 27 May 2019}

@@

\NOTE[LKC]{I have restructured the following paragraph.}

@@

\NOTE[DPF]{I thought we agreed to use BFSser throughout?  
In that sense it had emerged a few days ago, and now it has
re-emerged.  It is what we are going to use instead of ``current''.}
\NOTE[LKC]{I am confused. Do you mean we are going to use
	``BFS'' for the search strategy,
	``BFSser'' for Seres's BFS implementation, and
	``the improved BFS'' for our BFS implementation
?}

@@

\NOTE[LKC]{I have cited Boskin in the above paragraph.}

@@

\NOTE[LKC]{Following Boskin's suggestion, ``are ended with a thunk'' -> ``end 
with thunks''}

@@

\NOTE[LKC]{I have rewritten the sentence about \texttt{\#{}f}.}

@@

\NOTE[LKC]{(following Boskin's suggestion) constantly -> consistently}

@@

Our quantitative evaluation shows that \DFSbi{} is a competitive 
alternative to \DFSi{}, the current miniKanren search strategy,
and that \BFSimp{} is more practical than \BFSser{}.
We acknowledge that we are making large claims about efficiency given that we 
have just a few benchmarks, but our benchmarks cover some practically 
interesting cases (e.g. synthesizing expressions that evaluate to \texttt{'(I 
love you)}.

\NOTE[DPF]{Finish this paragraph with a clarification and you may
place this anywhere in the conclusion. This may require some consultation with 
Weixi.}
\NOTE[LKC]{Correcting.}

>>>>

\documentclass[format=acmlarge, review=false, authordraft=false]{acmart}

@@

@@

@@

@@

@@

@@

@@

@@

Our quantitative evaluation shows that \DFSbi{} is a competitive 
alternative to \DFSi{}, the current miniKanren search strategy,
and that \BFSimp{} is more practical than \BFSser{}.
We acknowledge that we are making large claims about efficiency given that we 
have just a few benchmarks, ...
